---
title: "CS112 8 MATCHING PreClass"
output: html_notebook
---
 

##Initial Data Setup and Exploration
###In-Sample observed treatment effect for each sample

Calculate the difference in means of the outcome (re78) in both samples.
Difference in means between Lalonde and NSW samples.
Are the estimated causal effects the same or similar? (Hint: they should not be the same, because the underlying treatment groups are very different.)


```{r}
setwd("~/Google Drive/Academics (Tomer)/0-2017 Buenos Aires Sem2.2/CS112 DataScience/R_CS112")
library(foreign)
library(Matching)
library(GGally)
library(ggplot2)
library(dplyr)
library(reshape2)
library(rgenoud)
library(faraway)

#opening Lalonde NSW Data Sample
nsw <- read.dta("/Users/tomereldor/Google Drive/Academics (Tomer)/0-2017 Buenos Aires Sem2.2/CS112 DataScience/R_CS112/nsw.dta")
attach(nsw)
#head(nsw)
#dim(nsw)

#opening DW Data Sample
dw <- read.dta("/Users/tomereldor/Google Drive/Academics (Tomer)/0-2017 Buenos Aires Sem2.2/CS112 DataScience/R_CS112/nsw_dw.dta")
#head(nsw)

#Calculate the difference in means of the outcome (re78) in both samples

#Lalonde Dateset difference in means
## divide the data into treated and control
nsw_treat <- nsw[treat == 1,]
nsw_control <- nsw[treat == 0,] 
#verify:
#nrow(nsw_treat) ; nrow(nsw_control) #check number of units

#calculate difference of means for NSW
print("NSW means: treat, control")
mean(nsw_treat$re78) ; mean(nsw_control$re78)
nsw_diff_means <- mean(nsw_treat$re78) - mean(nsw_control$re78)
#nsw_diff_means # = $886.3

#DW Dateset difference in means
## divide the data into treated and control
dw_treat <- dw[treat == 1,]
dw_control <- dw[treat == 0,] 
#na.omit(dw_control)
#verify
#nrow(dw_treat) ; nrow(dw_control) #check number of units
#dw_treat
#dw_control

#calculate difference of means for dw
print("DW means: treat, control")
mean(dw_treat$re78,na.rm=T) ; mean(dw_control$re78,na.rm=T)
dw_diff_means <- mean(dw_treat$re78) - mean(dw_control$re78,na.rm=T)
dw_diff_means # = $747.0836


##Difference in Means BETWEEN LALONDE to DW


#see both differences in means
print("-----") 
print("Lalonde diff means")
nsw_diff_means
print("DW diff means")
dw_diff_means

print("-----") 
print("Difference in Means BETWEEN LALONDE to DW")
diff_between_samples <- nsw_diff_means - dw_diff_means
diff_between_samples

```


Or: just in two lines, the difference of means
```{r}
# Calculate the difference in means of the outcome (re78) in both samples 

TEnsw <- mean(nsw[nsw$treat == 1,]$re78) -  mean(nsw[nsw$treat == 0,]$re78)   
TEdw <- mean(dw[dw$treat == 1,]$re78) -  mean(dw[dw$treat == 0,]$re78)  

TEnsw
TEdw
```




```{r}
print("Difference in Means BETWEEN LALONDE to DW")
diff_between_samples

##### t-test
print("t-test between samples")
t.test(nsw$re78,dw$re78)
print("t-test between treated in samples")
t.test(nsw_treat$re78,dw_treat$re78)

```




##Difference-in-means: pre-treatment covariates
run balance tests (t-tests) for key covariates. 
Are the covariates well-balanced?

```{r}


#run balance tests (t-tests) for key covariates. 

#nsw
MatchBalance((treat ~ education + re75 + age + black + hispanic + nodegree),data = nsw, ks=T, print.level = 1, nboots=500)

#dw
MatchBalance((treat ~ education + re75 + age + black + hispanic + nodegree), data = dw, ks=T, print.level = 1, nboots=500)


#run balance tests (t-tests) for key covariates 
#results show balance


#covariates MANUAL
cov <- c('education', 'black', 'age', 're75', 'nodegree')
nsw %>%
  group_by(treat) %>%
  select(one_of(cov)) %>%
  summarise_all(funs(mean(., na.rm = T)))  #funs = Create a list of functions calls ; 


```



Now download the PSID and CPS data files and attempt to use Mahalanobis, propensity score, and genetic matching to reconstruct a matched data set in R (e.g., matching nswre74_treated.txt), and you must use the ???Match???, ???GenMatch???, and ???MatchBalance??? functions???see the relevant help files. What are the properties of your matched data set? Are you able to recover the benchmark experimental estimate obtained in the randomized experiment?


##Mahalanobis Distance

```{r}
#setwd("~/Google Drive/Academics (Tomer)/0-2017 Buenos Aires Sem2.2/CS112 DataScience/R_CS112")
cps_controls <- read.dta("cps_controls.dta")
psid_controls <-  read.dta("psid_controls.dta")
nsw.treated <- read.table("nsw_treated.txt")

names(cps_controls)

cps_controls=cps_controls[2:10]
cov(cps_controls)
mahalanobis(x, colMeans(x), cov(x))



```



#Propensity Scores

```{r}

nsw.p <- nsw # copy lalonde for ps estimation

# generate propensity scores for all of the data in Lalonde 
ps.model <- glm(treat ~ age + education + black + nodegree + hispanic 
re75, data = nsw.p, family=binomial(link="logit"), na.action=na.pass)
 
summary(ps.model)
 
# add pscores to study data
nsw.p$pscore <- predict(ps.model, newdata = nsw.p, type = "response")
 
hist(nsw.p$pscore) # distribution of ps
summary(nsw.p$pscore)
dim(nsw.p)
 
# restrict data to ps range .10 <= ps <= .90

nsw.p2 <- nsw.p[nsw.p$pscore >= .10 & nsw.p$pscore <=.90,]
 
summary(nsw.p2$pscore)



```


##Genetic Matching

```{r}
# Append  the DW treated data to psid and cps -- why DW and not NSW? DW has re74 data, which psid and cps have

psidcombined <- psid
psidcombined <- rbind(dw[dw$treat == 1,],psidcombined)
psidcombined$treat <- psidcombined$treat == 1 # convert ones and zeroes to TRUE and FALSE (necessary for functions)

# Repeat for cps data

cpscombined <- cps
cpscombined <- rbind(dw[dw$treat == 1,],cpscombined)
cpscombined$treat <- cpscombined$treat == 1

```


```{r}
# Run genmatch to find weights that maximize balance betwen treatment and control groupsgenoutpsid <- GenMatch(Tr = 

genoutpsid <- GenMatch(Tr = psidcombined$treat, X = psidcombined[,3:10], BalanceMatrix = psidcombined[,3:10])
genoutcps <- GenMatch(Tr = cpscombined$treat, X = cpscombined[,3:10], BalanceMatrix = cpscombined[,3:10])
```


```{r}
# Now let's match -- create control groups from the PSID and CPS data WITH the genmatch output

matchedpsid.gm <- Match(Y = psidcombined$re78, Tr = psidcombined$treat, X = psidcombined[,3:10], M = 1, Weight.matrix = genoutpsid, BiasAdj=FALSE,sample = TRUE)

matchedcps.gm <- Match(Y = cpscombined$re78, Tr = cpscombined$treat, X = cpscombined[,3:10], M = 1, Weight.matrix = genoutcps,BiasAdj=FALSE,sample = TRUE)

matchedpsid.gm$est
matchedcps.gm$est

MatchBalance(psidcombined$treat~psidcombined$re78, data=psidcombined, match.out = matchedpsid.gm,nboots=500)
MatchBalance(cpscombined$treat~cpscombined$re78, data=cpscombined, match.out = matchedcps.gm,nboots=500)
```

```{r}
# Let's see how the match function performs in the absence of genetic matching

matchedpsid <- Match(Y = psidcombined$re78, Tr = psidcombined$treat, X = psidcombined[,3:10], M = 1, BiasAdj=FALSE,sample = TRUE)

matchedcps <- Match(Y = cpscombined$re78, Tr = cpscombined$treat, X = cpscombined[,3:10], M = 1,BiasAdj=FALSE,sample = TRUE)

matchedpsid$est
matchedcps$est

MatchBalance(psidcombined$treat~psidcombined$re78, data=psidcombined, match.out = matchedpsid,nboots=500)
MatchBalance(cpscombined$treat~cpscombined$re78, data=cpscombined, match.out = matchedcps,nboots=500)
```

#Propensity Scores Matching

```{r}
# Let's carry out propensity score matching

glmpsid <- glm(psidcombined$treat~psidcombined$age + psidcombined$black + psidcombined$hisp + psidcombined$nodegr + psidcombined$re74 + psidcombined$re75 + psidcombined$re78, family=binomial, data=psidcombined)

glmcps <- glm(cpscombined$treat~cpscombined$age + cpscombined$black + cpscombined$hisp + cpscombined$nodegr + cpscombined$re74 + cpscombined$re75 + cpscombined$re78, family=binomial, data=cpscombined)

matchedglmpsid <- Match(Y = psidcombined$re78, Tr = psidcombined$treat, X = glmpsid$fitted, M = 1,BiasAdj=FALSE,sample = TRUE)
matchedglmcps <- Match(Y = cpscombined$re78, Tr = cpscombined$treat, X = glmcps$fitted, M = 1,BiasAdj=FALSE,sample = TRUE)

matchedglmpsid$est
matchedglmcps$est

MatchBalance(psidcombined$treat~psidcombined$re78, data=psidcombined, match.out = matchedglmpsid,nboots=500)
MatchBalance(cpscombined$treat~cpscombined$re78, data=cpscombined, match.out = matchedglmcps,nboots=500)

```

